Efficient Handling of String-Number Conversion

### 2020-03-29 final-version/main.tex
set-up

\documentclass[sigplan,review,anonymous]{acmart}\settopmatter{printfolios=true,printccs=false,printacmref=false}

\usepackage{fancyvrb}
\usepackage{xcolor}
\usepackage{amssymb} 
\usepackage{tikz}
\usepackage[autostyle]{csquotes}
\usepackage{listings}
\usepackage{multirow}
\synctex=1
\usepackage{pgfplots}

\usetikzlibrary{positioning}
\usetikzlibrary{arrows,automata}
\sloppy

\title{Efficient Handling of String-Number Conversion}
\author{}

\begin{abstract}
String-number conversion is an important class of constraints needed for the symbolic execution of string-manipulating programs. In particular solving string constraints with string-number conversion  is necessary  for the analysis of scripting languages such as JavaScript and Python, where string-number conversion is a part of the definition of the core semantics of these languages. However, the state-of-the-art constraint solvers have only very limited support to this type of constraint. We propose to overcome these limitations with an approach that can efficiently support both string-number conversion and other common types of string constraints. Experimental results show that it significantly outperforms other state-of-the-art tools on benchmarks that involves string-number conversion.
\end{abstract}

>>>>

%% The first command in your LaTeX source must be the \documentclass command.
\documentclass[sigplan,screen]{acmart}

%%
%% \BibTeX command to typeset BibTeX logo in the docs
\AtBeginDocument{%
  \providecommand\BibTeX{{%
    \normalfont B\kern-0.5em{\scshape i\kern-0.25em b}\kern-0.8em\TeX}}}

%% Rights management information.  This information is sent to you
%% when you complete the rights form.  These commands have SAMPLE
%% values in them; it is your responsibility as an author to replace
%% the commands and values with those provided to you when you
%% complete the rights form.
\setcopyright{acmcopyright}
\acmPrice{}
\acmDOI{10.1145/3385412.3386034}
\acmYear{2020}
\copyrightyear{2020}
\acmSubmissionID{pldi20main-p869-p}
\acmISBN{978-1-4503-7613-6/20/06}
\acmConference[PLDI '20]{Proceedings of the 41st ACM SIGPLAN International Conference on Programming Language Design and Implementation}{June 15--20, 2020}{London, UK}
\acmBooktitle{Proceedings of the 41st ACM SIGPLAN International Conference on Programming Language Design and Implementation (PLDI '20), June 15--20, 2020, London, UK}

%%
%% Submission ID.
%% Use this when submitting an article to a sponsored event. You'll
%% receive a unique submission ID from the organizers
%% of the event, and this ID should be used as the parameter to this command.
%%\acmSubmissionID{123-A56-BU3}

%%
%% The majority of ACM publications use numbered citations and
%% references.  The command \citestyle{authoryear} switches to the
%% "author year" style.
%%
%% If you are preparing content for an event
%% sponsored by ACM SIGGRAPH, you must use the "author year" style of
%% citations and references.
%% Uncommenting
%% the next command will enable that style.
%%\citestyle{acmauthoryear}

%%
%% end of the preamble, start of the body of the document source.

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{microtype}

\usepackage{fancyvrb}
\usepackage{xcolor}
\usepackage{amssymb} 
\usepackage{tikz}
\usepackage[autostyle]{csquotes}
\usepackage{listings}
\usepackage{multirow}
\synctex=1
\usepackage{pgfplots}
\usetikzlibrary{positioning}
\usetikzlibrary{arrows,automata}
\sloppy

\title{Efficient Handling of String-Number Conversion}

\author{Parosh Aziz Abdulla}
\affiliation{
  \institution{Uppsala University}
    \state{Uppsala}
     \country{Sweden}                    %% \country is recommended           
}

\email{parosh@it.uu.se}

\author{Mohamed Faouzi Atig}
\affiliation{
  \institution{Uppsala University}
      \state{Uppsala}
    \country{Sweden}                    %% \country is recommended
}
\email{mohamed\_faouzi.atig@it.uu.se}

\author{Yu-Fang Chen}
\affiliation{
  \institution{Academia Sinica}
      \state{Taipei}
    \country{Taiwan}                    %% \country is recommended
}
\email{yfc@iis.sinica.edu.tw}

\author{Bui Phi Diep}
\affiliation{
  \institution{Uppsala University}
      \state{Uppsala}
    \country{Sweden}                    %% \country is recommended
}
\email{bui.phi-diep@it.uu.se}

\author{Julian Dolby}
\affiliation{
  \institution{IBM Research}
      \state{NY}
    \country{USA}                    %% \country is recommended
}
\email{bui.phi-diep@it.uu.se}

\author{Petr Janků}
\affiliation{
  \institution{Brno University of Technology}
      \state{Brno}
    \country{Czechia}                    %% \country is recommended
}
\email{ijanku@fit.vutbr.cz}

\author{Hsin-Hung Lin}
\affiliation{
  \institution{Academia Sinica}
      \state{Taipei}
    \country{Taiwan}                    %% \country is recommended
}
\email{hlin@iis.sinica.edu.tw}

\author{Lukáš Holík}
\affiliation{
  \institution{Brno University of Technology}
      \state{Brno}
    \country{Czechia}                    %% \country is recommended
}
\email{holik@fit.vutbr.cz}

\author{Hsin-Hung Lin}
\affiliation{
  \institution{University of Southern California}
      \state{CA}
    \country{USA}                    %% \country is recommended
}
\email{wwu@isi.edu}

\renewcommand{\shortauthors}{Abdulla, et al.}

\begin{abstract}
String-number conversion is an important class of constraints needed for the symbolic execution of string-manipulating programs. In particular solving string constraints with string-number conversion  is necessary  for the analysis of scripting languages such as JavaScript and Python, where string-number conversion is a part of the definition of the core semantics of these languages. However, the state-of-the-art constraint solvers have   limited support to this type of constraint. 
We propose to overcome these limitations with an approach that can efficiently support both string-number conversion and other common types of string constraints. Experimental results show that it significantly outperforms other state-of-the-art tools on benchmarks that involves string-number conversion.
\end{abstract}

\begin{CCSXML}
<ccs2012>
<concept>
<concept_id>10002978.10002986.10002990</concept_id>
<concept_desc>Security and privacy~Logic and verification</concept_desc>
<concept_significance>500</concept_significance>
</concept>
<concept>
<concept_id>10011007.10010940.10010992.10010998</concept_id>
<concept_desc>Software and its engineering~Formal methods</concept_desc>
<concept_significance>300</concept_significance>
</concept>
</ccs2012>
\end{CCSXML}

%\ccsdesc[500]{Theory of computation~Verification by model checking}
\ccsdesc[500]{Security and privacy~Logic and verification}
\ccsdesc[300]{Software and its engineering~Formal methods}
%% Keywords
%% comma separated list
\keywords{String Solver, Formal Verification, Automata}  %% \keywords are mandatory in final camera-ready submission
